The Expected Place of the Local Group in the Cosmic Web

### 2014-08-12 paper/main.tex
simulation and web finding algorithm

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
in the cosmic web as a peak, sheet, filament or void.  
The LG is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed in the LG.  
The second is a subset with additional kinematic constaints also
constrained by observations. 
We find that the pairs in the LG sample with all constraints are: (i)
preferentially   located in filaments and sheets, (ii) located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane. 
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignment with the cosmic web cannot be explained
by a simple mass dependency. 
This precise characterization of the expected place of the LG in the
cosmic web in a $\Lambda$CDM cosmology opens the door to a detailed
understanding of diverse features characterizing the Milky Way and the
Andromeda galaxies.

@@

Another feature of the Local group is the relatively low velocity
dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
  references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
Environment around the Local Group has density quite close to the
average density of the universe
\citep{2003ApJ...596...19K,2005AJ....129..178K}. 
In addition, the
closest massive galaxy cluster, the Virgo Cluster, is $\approx
16.5\ \mpc$ away \citep{2007ApJ...655..144M}.

All this combination of features make LG analogues rare to
find. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters.

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not enough to
challenge the \lcdm model.

Another definition of LG analogues is made by
\citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
definitions and resulting fraction of LG analogues, all are in
agreement with a low frequency of these pairs. 
%lw08 also look lg analogues

%larger scales & lg env
To better understand the properties of the LG and how this uncommon
pair configuration fit in the cosmological context, an immediate
question arise. What else can we say of the LG at larger scales?. In
particular, which are the typical/prefered locations of these systems
within the Cosmic Web?. To what extent is this an expected
configuration in $\Lambda$CDM.

Looking the LG at larger scales we have it is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group. At this scale, there is no evident alignment of the MW-M31
orbital plane with the local filament or the Virgo-Fornax
direction. However, if we look in a smaller volume below scales of
$\sim 6$ \mpc, there is a clear alignment of the MW-M31 orbit with
a local plane as shown by Figure $3$ in \citet{2013AJ....146...69C}.

%this paper.
In this \manuscript we study the large scale environment of LG 
analogues in the context of $\Lambda$CDM. We use the Bolshoi
simulation to explore in what structures they reside and if there is
any correlation or alignment with the cosmic web. The large scale
Environment is defined by the cosmic web components identified by
\citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}. We pay spetial attention to quantify the kind of
environment that hosts LG pairs and their alignments with respect to
the prefered directions defined by the T-web.

This \manuscript is organized as follows. In Section \ref{sec:simulation}
we present the N-body cosmological simulation and the algorithm to
define the cosmic web, next in \ref{sec:lg_analogues} we describe the
sample of LG analogues extracted from the simulation. In
Section \ref{sec:results} we presents our results to continue with a
discussion about their implications for our Local Group in Section
\ref{sec:discussion} to finally conclude in Section
\ref{sec:conclusions}.

@@

\cite{Tweb} performed a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. 
They found that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. 
In this \manuscript we choose the value of $\lambda_{\rm
  th}=0.3$ to proceed with our analysis. 
This is only relevant to the classification of the simulation into web
elements. Other results are completeley independent of this
choice. Nevertheless we have checked that the main conclusions of this
work do not depend on the choise of $\lambda_{\rm th}$.

@@

We also measure the alignment of the LG halos with respect to the
cosmic web defined by the eigenvector.
To this end we characterize each LG pair by two vectors. 
The first is $\hat{n}$, the vector marking the axis along the orbital angular
momentum of the pair, normal to its orbital plane; the second is
$\hat{r}$, the vector that connects the halos in the pair which can be
related to the alignment of the radial velocities to the web.
We quantify the alignment using the absolute value of the cosinus of
the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.

@@

\section{Discussion}
\label{sec:discussion}

@@

\section{Conclusions}
\label{sec:conclusions}

>>>>

\title{The Expected Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The LG is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed in the LG.  
The second is a subset with additional kinematic constaints also
constrained by observations. 
We find that the pairs in the LG sample with all constraints are: (i)
preferentially   located in filaments and sheets, (ii) located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
This precise characterization of the expected place of the LG in the
cosmic web in a $\Lambda$CDM cosmology opens the door to a detailed
understanding of diverse features characterizing the Milky Way and the
Andromeda galaxies.

@@

Another feature of the Local group is the relatively low velocity
dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
  references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
The environment around the Local Group has density quite close to the
average density of the universe
\citep{2003ApJ...596...19K,2005AJ....129..178K}. 
In addition, the closest massive galaxy cluster, the Virgo Cluster, is
$\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.

This combination of features make LG analogues rare to
find. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters. 
A similar abundance was found by \cite{ForeroRomero2011} by comparing the
formation history of LG pairs in constrained simulations with the
results of unconstrained cosmological simulations.

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not enough to
challenge the \lcdm model.  
Another definition of LG analogues is made
by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
definitions and resulting fraction of LG analogues, all are in
agreement with a low frequency of these pairs.

To better understand the properties of the LG and how this uncommon
pair configuration fit in the cosmological context, an immediate
question arise. 
What else can we say of the LG at larger scales?

Observationally, the LG is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group. 
At this scale, there is no evident alignment of the MW-M31 orbital
plane with the local filament or the Virgo-Fornax direction. However,
if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
a clear alignment of the MW-M31 orbit with a local plane as shown by
Figure $3$ in \citet{2013AJ....146...69C}.

We can then ask, to what extent is this an expected configuration in
$\Lambda$CDM? In particular, which are the typical/prefered locations
of these systems within the Cosmic Web?

%this paper.
In this \manuscript we study the large scale environment of LG 
analogues in the context of $\Lambda$CDM. 
We use the Bolshoi simulation to explore in what structures they
reside and if there is any correlation or alignment with the cosmic
web. 
The large scale environment is defined by the cosmic web components identified by
\citet{Tweb}, and we use the LG analogues computed by
\citet{lganalogues}.

This \manuscript is organized as follows. 
In Section \ref{sec:simulation}
we present the N-body cosmological simulation and the algorithm to
define the cosmic web, next in Section \ref{sec:lg_analogues} we describe the
sample of LG analogues extracted from the simulation. In
Section \ref{sec:results} we present our results to wrap up with a
discussion and conclusions in Section
\ref{sec:discussion}.

@@

\cite{Tweb} performed a detailed study for the topology of the
cosmic web and its visual counterpart as a function of the parameter
$\lambda_{\rm th}$. 
They found that reasonable results in terms of the
volume fraction occupied by voids, the visual inspection and the halo
populations in each web type can be reached by values of $0.2<\lambda_{\rm
th}<0.4$. 
In this \manuscript we choose the value of $\lambda_{\rm
  th}=0.3$ to proceed with our analysis. 
This is only relevant to the classification of the simulation into web
elements. Other results are completeley independent of this
choice. Nevertheless we have checked that the main conclusions of this
work do not depend on the precise choice of $\lambda_{\rm th}$.

@@

We also measure the alignment of the LG halos with respect to the
cosmic web defined by their eigenvectors.
To this end we characterize each LG pair by two vectors. 
The first is $\hat{n}$, the vector marking the axis along the orbital angular
momentum of the pair, normal to its orbital plane; the second is
$\hat{r}$, the vector that connects the halos in the pair which can be
related to the alignment of the radial velocities to the web.
We quantify the alignment using the absolute value of the cosinus of
the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.

@@

\section{Discussion and Conclusions}
\label{sec:discussion}

@@
